preprocessing

### 2022-10-24 r-prep/prep.Rmd
upd

data_base = data_gwp100 %>% left_join(data_wdi,by=c("ISO","year"))

@@

>>>>

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop)

@@

```{r}
load("data-raw/data_iea.RData")

data_kaya = data_base %>% 
  group_by(ISO,country,year,GDP_pc) %>% 
  summarise(CO2=sum(CO2,na.rm=TRUE)) %>%
  left_join(data_iea,data_iea,by=c("ISO","year")) %>%
  mutate(energy_intensity = energy/GDP_pc) %>%
  mutate(carbon_intensity = CO2/energy)

save(data_base,file="data-transf/data_kaya.RData")
```
